% !TEX program = xelatex

\documentclass[10pt]{stellingen}
\renewcommand\titlestyle[1]{{\LARGE\sffamily\MakeTextUppercase{#1}}}
\renewcommand\numberingstyle[1]{{\bfseries\sffamily #1}}
\renewcommand\sourcestyle[1]{{\footnotesize\emph{#1}}}
\renewcommand\stellingenstring{Propositions}
\renewcommand\behorendestring{to be defended along with the dissertation}
\setlength\topsep{0pt}

% FONTS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{fonts-inc.tex}

% PACKAGES %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[dutch,english]{babel}
% babel/polyglossia/mathspec workaround: github:fc7/polyglossia #28
\makeatletter
\begingroup
  \catcode`\"=\active
  \AtBeginDocument{\let"=\eu@active@quote}
\endgroup
\makeatother
% \usepackage[a4,center,frame]{crop} % for proofing - outline A5 page on A4 paper

% DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand\smallcaps[1]{{\scshape\MakeTextLowercase{#1}}}

\begin{document}

\title{Two-dimensional optics}
\author{Philip F.~Chimento}
\maketitle

% ABOUT THIS THESIS

\begin{stelling}[This thesis, chapter 3]
The topological charge of an optical field distribution in a transverse plane is distinct from the expectation value of the orbital angular momentum per photon, except in axial symmetry.
\end{stelling}

\begin{stelling}[This thesis, chapter 4]
Two nanoslits on a gold film could be used as a wavefront sensor with much higher spatial resolution than the commonly-used Shack-Hartmann sensor.
\end{stelling}

\begin{stelling}[This thesis, chapter 5]
The damping of a driven oscillator, and the conductivity of the metal in surface plasmon resonance, cause similar displacements of their maximum response.
\end{stelling}

\begin{stelling}[This thesis, chapter 5]
It is a misconception that the Otto configuration for studying surface plasmon resonances only causes difficulties.
\end{stelling}

% ABOUT THE FIELD OF PLASMONICS AND OPTICS

\begin{stelling}[Fridman et al.\ (2012). \emph{Nature 481}, 62.]
The temporal cloaking device will need to be paired with extremely slow light if it is to hide an event from human eyes.
\end{stelling}

\begin{stelling}[Couder et al.\ (2005). \emph{Nature 437}, 208.]
Walking droplets are a good illustration of pilot wave theory at a macroscopic scale.
\end{stelling}

\begin{stelling}
There is an advantage to cheap \smallcaps{CCD} cameras' lack of an infrared filter: one can use a laptop or mobile phone to check if one's \smallcaps{TV} remote is still working.
\end{stelling}

\begin{stelling}[Horv\'ath et al.\ (2010). An unexpected advantage of whiteness in horses: the most horsefly-proof horse has a depolarizing white coat. \emph{Proc.\ R.\ Soc.\ B 277}, 1643.]
There is a correlation between an object's color and the degree of polarization of the light it scatters.
\end{stelling}

% ABOUT WHATEVER

% \begin{stelling}[Gottschall \& Gottschall (2003). Are per-incident rape-pregnancy rates higher than per-incident consensual pregnancy rates? \emph{Human Nature 14}(1), 1--20; Renfree \& Shaw (2000). Diapause. \emph{Ann.\ Rev.\ Physiology 62}(1), 353--375.]
% Politicians who base their anti-abortion stance on `ways of shutting that whole thing down' are apparently confusing humans and kangaroos.
% The suggestion that women's reproductive organs can be `shut down' at will doesn't account for the very real differences between humans and kangaroos.
% \end{stelling}

\begin{stelling}[Foremski (2005, June 10). Exclusive interview with seminal 1960s computer visionary Doug Engelbart. \emph{Silicon Valley Watcher.}]
The data cloud could have been developed forty years ago, had it not been for the baby boomers' distrust of centralization.
\end{stelling}

\begin{stelling}[Amiss \& Abbott (1995). \emph{Method of exercising a cat.} United States Patent No.\ 5443036.]
One can use a laser pointer to probe a cat's mechanical excitation states and their eigenfrequencies.
\end{stelling}

% \begin{stelling}[Article 18.7 of Promotiereglement Universiteit Leiden 2008]
% Prohibiting advertising in dissertations runs counter to the Dutch government's policy of shifting the burden of science funding to industry.
% (For example, I would have had Heinz Plasmon Biscuits sponsor the front cover of this dissertation.)
% \end{stelling}

% \begin{stelling}
% Given \smallcaps{LION}'s objective of bringing gifted students into contact with `real' research at the earliest possible stage, the undergraduate curriculum makes no sense: students learn to analyze their data in Origin.
% \end{stelling}

% \begin{stelling}
% Writing a paper together after a public disagreement in the literature is the professor's equivalent of make-up sex. \emph{Corollary:} Those are always the best papers.
% \end{stelling}

\begin{stelling}
Scientists who don't trust students' possibly clumsy hands on their research should work at a research institute instead of at a university.
\end{stelling}

% \begin{stelling}
% No amount of effort to increase the share of female professors will help, when old goats are still free to make young women feel unwelcome in physics.
% \end{stelling}

\end{document}